Different centralities in multilayer stream graphs

### 2019-07-30 tex/article/main.tex
Compresser les figures en une superfigure

@@

To illustrate the definitions of all the graphs, we will use the same example: a population of monkeys $F_1, F_2, M_1, M_2$ (two females and two males). In the \cref{fig:graphsimple}, we put a link between two animals if they have been in contact.

\begin{figure}[h]
			\begin{center}
					\begin{tikzpicture}[xscale=2,yscale=2,auto]
							\draw (1,0) node[VertexStyle]   (A) { $F_1$ };
							\draw (0,0) node[VertexStyle] (B) { $F_2$ };
							\draw (0,1) node[VertexStyle]   (C) { $M_1$ };
							\draw (1,1) node[VertexStyle]   (D) { $M_2$ };

@@

					\end{tikzpicture}
			\end{center}
	\caption{An example of undirected graph. The nodes $V=(F_1, F_2, M_1, M_2)$ are monkeys, and the undirected edges $E=(M_1,M_2),(M_1,F_1),(M_1,F_2),(F_1,F_2)$ represent the fact that they have been in contact.}
	\label{fig:graphsimple}
\end{figure}

In the monkeys example \cref{multimonkeys}, the nodes are still the monkeys. The structure is made of two aspects: the place and the type of interaction. A layer can be for instance (mountain,collaboration). They are different types of links, depending on which layer are the nodes.

\begin{equation}
\begin{array}{rcl}
  {\cal L}&=&\{\text{place},\text{type of relationship}\} \\
  \text{place} &=& \{\text{mountain, plane}\}\\
 \text{type of relationship} &=& \{ \text{fight,collaboration}\}
\end{array}
\end{equation}
%0.58

\begin{figure}[h]
\begin{center}
\begin{tikzpicture}[scale=0.38,every node/.style={minimum size=1cm},on grid]

@@

	%interlayer
	\draw[thick, dashed, decorate] (-1.6,5.2) to[bend left] (8.4,10.2);%C
	\draw[thick, dashed, decorate] (3.2,4.7) to[bend left] (13.2,9.7);%A
	\draw[thick, dashed, decorate] (1.5,6.8) to[bend left] (11.4,11.7);%D
\end{tikzpicture}
\caption{The multilayer graph of relationships between monkeys. Red link between $M_1$ and $F_2$ means that the two monkeys have been fighting in the forest. The dotted links means that the nodes-layers are from the same nodes.}
\label{multimonkeys}
\end{center}
\end{figure}

@@

In the \cref{exmonkeystream}, we give an example of stream graph for the monkey population. We look at a place (let's say the forest) and we put a link between two monkeys when they interact.

\begin{figure}
\centering
	\includegraphics[width=0.5\textwidth]{img/ext.pdf}
	\caption{Example of stream graph describing interactions between monkeys in the forest. $F_1$ arrives at $t=3$, and interacts with $F_2$ at $t \in[4,5]\cup [7,8]$. $F_2$ and $M_1$ interact between $t=2$ and $4$.}
	\label{exmonkeystream}
\end{figure}

@@

   We give an example of modelisation for the imaginary multilayer stream graph of relationships between monkeys, \cref{multistreamMonkeys}.
   \begin{figure}[h]
   	\includegraphics[width=0.8\textwidth]{img/monkeymls.pdf}
   	\caption{An example of the 2-layers stream graph of monkeys, collaborating in mountain or in plain. $F_1$ is in [mountain, collaboration] between $t=0$ and $t=4$ and then goes to [plain,collaboration]. It collaborates with $F_2$ at $t\in [1,2]\cup[3,4]$: $\{(t,F_1,[\text{mountain,collaboration}],F_2,[\text{mountain,collaboration}]),t\in [1,2]\cup[3,4]\} \subset E_M$.}
   	\label{multistreamMonkeys}
   \end{figure}

@@

\begin{definition}[Induced multilayer graph]
    The {\em induced multilayer graph by the set } $\tau \subseteq T$ is a multilayer graph $M_I(S_M)=(V_{M,I}, E_{M,I}, V,L)$ which gathers all the layers, nodes-layers and links existing during a time of $\tau$.
    \begin{align*}
    	V_{M,I} = \{ v \in V | \exists t \in \tau, (t,v) \in V_M\}\\
    	E_{M,I} = \{((v,\alpha),(w,\beta)) \in (V\times L)\otimes (V\times L) | \exists t \in \tau , (t,v,\alpha,w,\beta) \in E_M \} \\
    \end{align*}
    In our example of monkeys, the lower part of \cref{multimonkeys} is the induced multilayer stream graph of the multilayer stream graph represented \cref{multistreamMonkeys}.
\end{definition}

>>>>

% Subfloat
\usepackage{subcaption}
\captionsetup{compatibility=false}

@@

To illustrate the definitions of all the graphs, we will use the same example: a population of monkeys $F_1, F_2, M_1, M_2$ (two females and two males). In the \cref{subfig:monkeysimple}, we put a link between two animals if they have been in contact.

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.35\textwidth}
			\centering
			\begin{tikzpicture}[xscale=2,yscale=1.25,auto]
										\draw (1,0) node[VertexStyle]   (A) { $F_1$ };
										\draw (0,0) node[VertexStyle] (B) { $F_2$ };
										\draw (0,1) node[VertexStyle]   (C) { $M_1$ };
										\draw (1,1) node[VertexStyle]   (D) { $M_2$ };

@@

								\end{tikzpicture}
				\caption{An example of undirected graph. The nodes $V=(F_1, F_2, M_1, M_2)$ are monkeys, and the undirected edges $E=(M_1,M_2)$, $(M_1,F_1)$, $(M_1,F_2)$, $(F_1,F_2)$ represent the fact that they have been in contact.}
				\label{subfig:monkeysimple}
    \end{subfigure}
    \hfill%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.6\textwidth}
				\includegraphics[width=\textwidth]{img/ext.pdf}
				\caption{Example of stream graph describing interactions between monkeys in the forest. $F_1$ arrives at $t=3$, and interacts with $F_2$ at $t \in[4,5]\cup [7,8]$. $F_2$ and $M_1$ interact between $t=2$ and $4$.}
				\label{subfig:monkeystream}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
    %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{\textwidth}
			\centering
			\begin{tikzpicture}[scale=0.38,every node/.style={minimum size=1cm},on grid]

@@

				%interlayer
				\draw[thick, dashed, decorate] (-1.6,5.2) to[bend left] (8.4,10.2);%C
				\draw[thick, dashed, decorate] (3.2,4.7) to[bend left] (13.2,9.7);%A
				\draw[thick, dashed, decorate] (1.5,6.8) to[bend left] (11.4,11.7);%D
			\end{tikzpicture}
			\caption{The multilayer graph of relationships between monkeys. Red link between $M_1$ and $F_2$ means that the two monkeys have been fighting in the forest. The dotted links means that the nodes-layers are from the same nodes.}
			\label{subfig:monkeyplex}
    \end{subfigure}
    \caption{Monkeys interactions through the lens of different kind of networks.}\label{fig:monkey}
\end{figure}

In the monkeys example \cref{subfig:monkeyplex}, the nodes are still the monkeys. The structure is made of two aspects: the place and the type of interaction. A layer can be for instance (mountain,collaboration). They are different types of links, depending on which layer are the nodes.

\begin{equation}
\begin{array}{rcl}
  {\cal L}&=&\{\text{place},\text{type of relationship}\} \\
  \text{place} &=& \{\text{mountain, plane}\}\\
 \text{type of relationship} &=& \{ \text{fight,collaboration}\}
\end{array}
\end{equation}

@@

In the \cref{subfig:monkeystream}, we give an example of stream graph for the monkey population. We look at a place (let's say the forest) and we put a link between two monkeys when they interact.

@@

   We give an example of modelisation for the imaginary multilayer stream graph of relationships between monkeys, \cref{multistreamMonkeys}.
   \begin{figure}[t!]
   	\includegraphics[width=0.6\textwidth]{img/monkeymls.pdf}
   	\caption{An example of the 2-layers stream graph of monkeys, collaborating in mountain or in plain. $F_1$ is in [mountain, collaboration] between $t=0$ and $t=4$ and then goes to [plain,collaboration]. It collaborates with $F_2$ at $t\in [1,2]\cup[3,4]$: $\{(t,F_1,[\text{mountain,collaboration}],F_2,[\text{mountain,collaboration}]),t\in [1,2]\cup[3,4]\} \subset E_M$.}
   	\label{multistreamMonkeys}
   \end{figure}

@@

\begin{definition}[Induced multilayer graph]
    The {\em induced multilayer graph by the set } $\tau \subseteq T$ is a multilayer graph $M_I(S_M)=(V_{M,I}, E_{M,I}, V,L)$ which gathers all the layers, nodes-layers and links existing during a time of $\tau$.
    \begin{align*}
    	V_{M,I} & = \{ v \in V | \exists t \in \tau, (t,v) \in V_M\}\\
    	E_{M,I} & = \{((v,\alpha),(w,\beta)) \in (V\times L)\otimes (V\times L) | \exists t \in \tau , (t,v,\alpha,w,\beta) \in E_M \} \\
    \end{align*}
    In our example of monkeys, the lower part of \cref{subfig:monkeyplex} is the induced multilayer stream graph of the multilayer stream graph represented \cref{multistreamMonkeys}.
\end{definition}
